An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-25 EconGrowth.Rnw
Edited the to-do list.

\section*{To-do List}
\begin{itemize}
\item Reese: Add text from Word verson of paper to the LaTeX version.
\item Heun: Add CES production function fits
      \begin{itemize}
      \item \st{GDP comparison graph}
      \item \st{Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.}
      \item \st{Create parameter graphs for each country}
      \item \st{Parameter tables for each energy type in the appendix}
      \item \st{Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix}
      \item AIC rows in the AIC table
      \end{itemize}
\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command.
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
      \begin{itemize}
      \item Zambia, upper bound on $c_t$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
\item de Wit: provide funding acknowledgement, if necessary.
\item de Wit: review, critique, and contextualize.
\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: Move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\item \st{Heun: Add single factor fits}
      \begin{itemize}
      \item \st{Correct sizes for parameter graphs for each country}
      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{GDP comparison graph}
      \item \st{AIC rows in the AIC table}
      \end{itemize}
\item \st{Heun: Add setup variables for figure height and width where not already included.}
\item \st{Heun: Add LINEX production function fits}
      \begin{itemize}
      \item \st{Parameter graphs for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{AIC rows in the AIC table}
      \item \st{GDP comparison graph}
      \end{itemize}
\end{itemize}

>>>>

\section*{To-do List}
\begin{itemize}
\item Reese: Add text from Word verson of paper to the LaTeX version.
\item Heun: Add CES production function fits
      \begin{itemize}
      \item \st{GDP comparison graph}
      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
      \item Write up the decisions about parameter estimation for the CES production function fits
      \item \st{Create parameter graphs for each country}
      \item \st{Parameter tables for each energy type in the appendix}
      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
      \item AIC rows in the AIC table
      \end{itemize}
\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command.
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
      \begin{itemize}
      \item Zambia, upper bound on $c_t$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
\item de Wit: provide funding acknowledgement, if necessary.
\item de Wit: review, critique, and contextualize.
\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: Move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\item \st{Heun: Add single factor fits}
      \begin{itemize}
      \item \st{Correct sizes for parameter graphs for each country}
      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{GDP comparison graph}
      \item \st{AIC rows in the AIC table}
      \end{itemize}
\item \st{Heun: Add setup variables for figure height and width where not already included.}
\item \st{Heun: Add LINEX production function fits}
      \begin{itemize}
      \item \st{Parameter graphs for each country}
      \item \st{Parameter tables for each country in the appendix}
      \item \st{AIC rows in the AIC table}
      \item \st{GDP comparison graph}
      \end{itemize}
\end{itemize}
